### 2022-11-09 doc/manuscript/translocation.qmd
Add figures to translocation section

@@

We used exome capture methods to compare genomes of frogs in populations with different histories of Bd exposure, in an effort to identify putative genes under selection that are linked to reduced frog susceptibility to Bd-caused lethal and sub-lethal effects. Specifically, we compared genomes of frogs that have never experienced a Bd-caused epizootic ("Bd-naive") versus populations that experienced a Bd epizootic during the past several decades and have since recovered to varying degrees ("recovering). These populations persist in an enzootic state, characterized by high Bd prevalence and Bd infection intensities (load) in adults that are well below the level expected to cause frog mortality. Bd-exposure histories of these populations are based on a decade or more of data from VES and Bd surveillance using skin swabbing.

@@

DNA samples were collected via buccal swabbing of xx-xx frogs from seven Bd-naive populations <!--# Dusy 10220 not included due to small sample size? --> and seven recovering populations. These populations represented a wide latitudinal range in the southern Sierra Nevada from northern Yosemite National Park to south of Sequoia National Park (Figure Sx), and the latitudinal range of the two population types was similar.

<!--# Create map of sample sites -->

@@

>>>>

Results text will be added soon. Figure XX is likely to be included in the main manuscript, and Figure XXX will probably be moved to the Supplementary Information.

![Figure XX. Average survival of each cohort of translocated frogs to the 12 recipient sites included in this study. Sites are arranged along the x-axis using the average of the median survival per translocation. Frog survival for the one-year period following each transloation was estimated using capture-mark-recapture methods. Dot colors indicate the donor population from which frogs in each translocated cohort were collected.](figures/translocation_survival_bysiteid.png)

![Figure XXX. For the best model predicting frog survival following translocations, 95% uncertainty intervals for the coefficients of each predictor variable. Uncertainty intervals are shown as shaded areas under the estimated posterior density curve. Posterior medians are indicated by the verical line in each curve. Important predictors of frog survival are those for which the uncertainty interval does not include zero (vertical red dashed line). Bd load at the time of translocation did not affect subsequent frog survival.](figures/mcmc_areas_m1d.png)

@@

We used exome capture methods to compare genomes of frogs in populations with different histories of Bd exposure, in an effort to identify putative genes under selection that are linked to reduced frog susceptibility to Bd-caused lethal and sub-lethal effects. Specifically, we compared genomes of frogs that have never experienced a Bd-caused epizootic ("Bd-naive") versus populations that experienced a Bd epizootic during the past several decades and have since recovered to varying degrees ("recovering"). These populations persist in an enzootic state, characterized by high Bd prevalence and Bd infection intensities (load) in adults that are well below the level expected to cause frog mortality. Bd-exposure histories of these populations are based on a decade or more of data from VES and Bd surveillance using skin swabbing.

@@

DNA samples were collected via buccal swabbing of xx-xx frogs from seven Bd-naive populations and seven recovering populations. These populations represented a wide latitudinal range in the southern Sierra Nevada from northern Yosemite National Park to south of Sequoia National Park (Figure SXXXX), and the latitudinal range of the two population types was similar.

![Figure SXXXX. Map showing the locations of Bd-naive or recovering frog populations from which DNA samples were collected for the exome capture analyses. To obscure the exact locations of populations, random noise was added to all point coordinates. Black polygons indicate the boundaries of Yosemite, Kings Canyon, and Sequoia national parks (from top to bottom).](figures/map_exome_points.png)

@@

<!--# Add modeling methods -->
